Rmd to HTML

### 2017-01-31 inst/examples/joss.Rmd
Update on JOSS paper submission.

```{r symm, echo = FALSE}
library(dplyr)
library(highlightHTML)

@@

table_id_inject(chick_tab, id = c('#bggrey', '#bgblack'), 
                conditions = c('> 270', '> 300'),
                variable = list('avg_weight', 'avg_weight'))
```

>>>>

```{r symm, echo = FALSE, results = 'asis'}
library(dplyr)
library(highlightHTML)

@@

knitr::kable(table_id_inject(chick_tab, id = c('#bggrey', '#bgblack', '#bglightred'), 
                conditions = c('> 270', '> 300', '> 60'),
                variable = list('avg_weight', 'avg_weight', 'sd_weight')),
             format = 'markdown')
```
